\section{Requisitos}

A continuación, se describen los requisitos del sistema a desarrollar, incluyendo la calidad del mismo.


% \requirement{<id>}{<description>}{<quality>}
\newcommand{\requirement}[3]{%
\begin{table}[htbp]
  \centering
  \noindent
  \begin{tabular}{@{}p{83pt}@{}p{.85\columnwidth-83pt}@{}}
    \toprule
    \multicolumn{2}{@{}l}{\bfseries{#1}} \\
    \hline
    \textbf{Description}   & {#2} \\
    \textbf{Quality Level} & {#3} \\
    \bottomrule
  \end{tabular}
  \caption{Requirement #1}
  \label{req:#1}
\end{table}
}



% enable obscene amount of tables without breaks
\maxdeadcycles=200
\extrafloats{50}



\requirement{REQ-01}
  {
    The system shall allow users to complete the purchase providing visual guidance.
  }
  {High}

\requirement{REQ-02}
  {
    The system shall include the filter of products.
  }
  {Medium}

\requirement{REQ-03}
  {
    The system shall display the guided process for configuring the products.
  }
  {Medium}

\requirement{REQ-04}
  {
    The system shall validate user-provided data accuracy, using predefined rules before allowing the confirmation of the transaction.
  }
  {Medium}

\requirement{REQ-05}
  {
    The system shall allow users to upload PDF files up to 5MB in size.
  }
  {Medium}

\requirement{REQ-06}
  {
    The system shall generate the digital receipt confirming the selected configuration.
  }
  {Medium}

\requirement{REQ-07}
  {
    The system shall display the status of the order in real time, with updates upon user refresh.
  }
  {Medium}

\requirement{REQ-08}
  {
    The system shall provide the activity log.
  }
  {High}

\requirement{REQ-09}
  {
    The system shall allow users to cancel the configuration before final confirmation.
  }
  {High}

\requirement{REQ-10}
  {
    The system shall notify users of progress via the status bar.
  }
  {Medium}

\requirement{REQ-11}
  {
    The system shall provide users with messages when errors occur.
  }
  {High}

\requirement{REQ-12}
  {
    The system shall save partially completed configuration automatically.
  }
  {Medium}

\requirement{REQ-13}
  {
    The system shall allow users to load the previously saved configuration.
  }
  {High}

\requirement{REQ-14}
  {
    The system shall restrict access to configuration data.
  }
  {Medium}

\requirement{REQ-15}
  {
    The system shall be accessible via web.
  }
  {High}

\requirement{REQ-16}
  {
    The system shall support responsive layout.
  }
  {High}

\requirement{REQ-17}
  {
    The system shall log configuration sessions.
  }
  {Medium}

\requirement{REQ-18}
  {
    The system shall export the final configuration to the PDF file.
  }
  {Medium}

\requirement{REQ-19}
  {
    The system shall support multilingual interface.
  }
  {High}

\requirement{REQ-20}
  {
    The system shall deny submission of incomplete configurations.
  }
  {High}

\requirement{REQ-21}
  {
    The system shall notify the user when selecting incompatible components.
  }
  {High}

\requirement{REQ-22}
  {
    The system shall calculate the total cost of the configuration.
  }
  {Medium}

\requirement{REQ-23}
  {
    The system shall integrate with the payment gateway.
  }
  {High}

\requirement{REQ-24}
  {
    The system shall store the completed configuration in the secure database.
  }
  {Medium}

\requirement{REQ-25}
  {
    The system shall allow administrators to modify component prices.
  }
  {Medium}

\requirement{REQ-26}
  {
    The system shall support uploading of component images.
  }
  {Medium}

\requirement{REQ-27}
  {
    The system shall provide tool tips for the configuration options.
  }
  {High}

\requirement{REQ-28}
  {
    The system shall allow components to be grouped into predefined templates.
  }
  {High}

\requirement{REQ-29}
  {
    The system shall display the visual representation of the current configuration.
  }
  {Medium}

\requirement{REQ-30}
  {
    The system shall track the environmental impact of each configuration.
  }
  {Medium}

\requirement{REQ-31}
  {
    The system shall allow users to compare up to 3 configurations.
  }
  {High}

\requirement{REQ-32}
  {
    The system shall offer assistance through the chatbot.
  }
  {Medium}

\requirement{REQ-33}
  {
    The system shall detect deprecated components.
  }
  {Medium}

\requirement{REQ-34}
  {
    The system shall require users to confirm legal terms.
  }
  {High}

\requirement{REQ-35}
  {
    The system shall allow users to submit feedback on the configuration.
  }
  {High}

\requirement{REQ-36}
  {
    The system shall automatically send the confirmation email with the configuration summary.
  }
  {Medium}

\requirement{REQ-37}
  {
    The system shall allow users to duplicate the existing configuration.
  }
  {High}

\requirement{REQ-38}
  {
    The system shall be operational 99\% of the time.
  }
  {Medium}

\requirement{REQ-39}
  {
    The system shall apply discounts dynamically.
  }
  {High}

\requirement{REQ-40}
  {
    The system shall comply with the general data protection regulation.
  }
  {Medium}

\requirement{REQ-41}
  {
    The system shall support custom themes.
  }
  {High}

\requirement{REQ-42}
  {
    The system shall support browser navigation without losing selected configuration data.
  }
  {Medium}

\requirement{REQ-43}
  {
    The system shall log out users automatically after 15 minutes of inactivity.
  }
  {Medium}

\requirement{REQ-44}
  {
    The system shall store configuration changes in version history.
  }
  {Medium}

\requirement{REQ-45}
  {
    The system shall integrate with external software by exporting configuration data.
  }
  {High}

\requirement{REQ-46}
  {
    The system shall allow authorized users to mark configurations as 'pending approval'.
  }
  {Medium}

\requirement{REQ-47}
  {
    The system shall prevent simultaneous editing of the same configuration.
  }
  {High}

\requirement{REQ-48}
  {
    The system shall validate numeric input fields to allow only valid values within defined ranges.
  }
  {Medium}

\requirement{REQ-49}
  {
    The system shall allow saving notes.
  }
  {High}

\requirement{REQ-50}
  {
    The system shall allow exporting configuration data.
  }
  {High}
